Proportional multi-state multiple-cohort life table model

### 2018-05-02 MSLT/MSLTdoc.Rmd
Generate age, sex and outcome specific group plots

i_outcome <- c("mx", "inc")
p_list <- list()

index <- 1
for (age in i_age_cohort){
  for (sex in i_sex) {
     for (disease in i_disease){
       for (outcome in i_outcome) {
         {
       if (sex == "male" && disease == "breast_cancer"){
         # cat("\n")
       }else{

p_index  <- plot_output(in_data = output_df, in_age = age, in_population = sex, in_outcomes = c("age", paste(outcome, "num", "bl", disease, sep = "_"), paste(outcome, "num", "sc", disease, sep = "_"), paste(outcome, "num", "diff", disease, sep = "_")), in_legend = paste(outcome, disease, sep = " "))

p_list[[index]] <- p_index
index <- index + 1

            }
         }
       }
     }
   }
}

@@

mpage <- do.call(marrangeGrob, list(grobs=p_list, nrow = 3, ncol = 2))
mpage

>>>>

require(ggplot2)
require(gridExtra)
require(grid)

grid_arrange_shared_legend <- function(..., ncol = length(list(...)), nrow = 1, position = c("bottom", "right"), mainTitle = "", mainLeft = "", mainBottom = "") {

  plots <- list(...)
  position <- match.arg(position)
  g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  lwidth <- sum(legend$width)
  gl <- lapply(plots, function(x) x + theme(legend.position="none"))
  gl <- c(gl, ncol = ncol, nrow = nrow, top = mainTitle, left = mainLeft, bottom = mainBottom)

  combined <- switch(position,
                     "bottom" = arrangeGrob(do.call(arrangeGrob, gl),
                                            legend,
                                            ncol = 1,
                                            heights = unit.c(unit(1, "npc") - lheight, lheight)),
                     "right" = arrangeGrob(do.call(arrangeGrob, gl),
                                           legend,
                                           ncol = 2,
                                           widths = unit.c(unit(1, "npc") - lwidth, lwidth)))

  #grid.newpage()
  grid.draw(combined)

  # return gtable invisibly
  invisible(combined)

g_legend <- function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}

output_dir = "graphs"

i_outcome <- c("mx", "inc")
p_list_male <- list()
p_list_female <- list()
male_index <- 1
female_index <- 1
for (age in i_age_cohort){
      for (sex in i_sex) {
        for (outcome in i_outcome) {
          for (disease in i_disease){

       if (sex == "male" && disease == "breast_cancer"){
         # cat("\n")
       }else{

            p_index  <- plot_output(in_data = output_df, in_age = age, in_population = sex, in_outcomes = c("age", paste(outcome, "num", "bl", disease, sep = "_"), paste(outcome, "num", "sc", disease, sep = "_"), paste(outcome, "num", "diff", disease, sep = "_")), in_disease = disease)

            if (sex == "male"){

              p_list_male[[male_index]] <- p_index

              if (male_index %% 4 == 0 && male_index > 0){

                p1 <- p_list_male[[male_index - 3]] + theme(legend.position="none", axis.title.x = element_blank(),  axis.title.y = element_blank())
                p2 <- p_list_male[[male_index - 2]] + theme(legend.position="none", axis.title.x = element_blank(),  axis.title.y = element_blank())
                p3 <- p_list_male[[male_index - 1]] + theme(legend.position="none", axis.title.x = element_blank(),  axis.title.y = element_blank())
                p4 <- p_index + theme(legend.position="none", axis.title.x = element_blank(),  axis.title.y = element_blank())

                pdf(paste0(output_dir, "/", paste(age, sex, outcome, sep="_"), ".pdf"))
                grid_arrange_shared_legend (p1, p2, p3, p4, ncol = 2, nrow = 2, mainTitle = paste(age, sex, outcome),
                                          mainLeft = 'Cases', mainBottom = 'Age')
                dev.off()

              male_index <- male_index + 1

            if (sex == "female" && female_index > 0){
              p_list_female[[female_index]] <- p_index

              if (female_index %% 5 == 0){
                p1 <- p_list_female[[female_index - 4]] + theme(legend.position="none", axis.title.x = element_blank(),  axis.title.y = element_blank())
                p2 <- p_list_female[[female_index - 3]] + theme(legend.position="none", axis.title.x = element_blank(),  axis.title.y = element_blank())
                p3 <- p_list_female[[female_index - 2]] + theme(legend.position="none", axis.title.x = element_blank(),  axis.title.y = element_blank())
                p4 <- p_list_female[[female_index - 1]] + theme(legend.position="none", axis.title.x = element_blank(),  axis.title.y = element_blank())
                p5 <- p_index + theme(legend.position="none", axis.title.x = element_blank(),  axis.title.y = element_blank())

                pdf(paste0(output_dir, "/", paste(age, sex, outcome, sep="_"), ".pdf"))
                grid_arrange_shared_legend (p1, p2, p3, p4, p5, ncol = 2, nrow = 3, mainTitle = paste(age, sex, outcome),
                                            mainLeft = 'Cases', mainBottom = 'Age')
                dev.off()

              }
              female_index <- female_index + 1
            }

            }
         }
       }
   }
}

@@

# mpage_male <- do.call(marrangeGrob, list(grobs=p_list_male, nrow = 2, ncol = 2))
# mpage_male
# 
# 
# lay <- rbind(c(1, 2),
#              c(3, 4),
#              c(5, NA))
# 
# 
# mpage_female <- do.call(marrangeGrob, list(grobs=p_list_female, layout_matrix = lay))
# mpage_female
